---
title: "Read OneDrive"
author: "Richard Sprague"
date: "6/4/2022"
output: github_document
---

# Read and Write to OneDrive

An [announcement by Hong](https://community.rstudio.com/t/microsoft365r-interface-to-microsoft-365-sharepoint-onedrive-etc/94287) at the RStudio Community Site points me to a library that can read and write to Microsoft 365 resources, including OneDrive. Is this my solution for reading Excel files online?

First I install the package (if necessary) and get a pointer to my personal OneDrive.

```{r setup, message = FALSE}
library(tidyverse, quietly = TRUE)
if(!require("Microsoft365R")) install.packages("Microsoft365R")

od <- Microsoft365R::get_personal_onedrive()

```

The first time this is run, it will open a browser for you and ask for your Microsoft 365 credentials.

```{r fileplay}
od$list_items() %>% tail() %>% select(name, size, isdir)
```

## Read an Excel file

I keep a copy of my health-related self-tracking in a complicated Excel file. Let's confirm that it's there.

```{r, seeFiles}
trackfilepath <- file.path("General/Health/Richard_Sprague_Tracking.xlsx")

trackfile_item_list <- od$get_item_properties(trackfilepath)
trackfile_item_list[["name"]]
trackfile_item_list[["createdBy"]]

```

and now try to read it. It's easy to open it into a browser.

```{r readExcelWeb}

if(interactive()) od$open_item(trackfilepath) else "(shows in browser)"

```

To read it into a dataframe requires some roundabout action. I can grab the URL easily enough, but it appears I must then read the contents using `curl`.  Unfortunately that requires I make a separate, local copy of the file.

```{r readExcel}
trackfile_url <- trackfile_item_list[["@microsoft.graph.downloadUrl"]]

destfile <- "tempCopy.xlsx"
curl::curl_download(trackfile_url, destfile)
Richard_Sprague_Tracking <- readxl::read_xlsx(destfile)

head(Richard_Sprague_Tracking)[1:3]

```

But it works! and unlikely my [previous hack](https://richardsprague.com/post/2019/09/20/r-tude-read-onedrive-excel-files/) this one may preserve the correct URL across sessions.  #betterThanNothingIguess




