---
title: "Viome Recommendations"
format: 
   html:
     df-print: paged
---

## Problem

You have an Excel table of previous Viome food recommendations and you'd like to see which ones have changed.

The table looks like this:

| Food      | Oct-22    | Oct-20    | May-20 |
|-----------|-----------|-----------|--------|
| Abalone   | Enjoy     | Enjoy     | Enjoy  |
| Anchovies | Superfood | Superfood | Enjoy  |
| Apple     | Enjoy     | Avoid     | Enjoy  |

: Viome Recommendations\

I want to generate a table showing just those rows that changed. Ideally, I'll turn this into a simple plot showing how specific food recommendations change over time.

Read everything into a dataframe.

```{r setup_viome}
#| echo: false
#| warning: false
#| message: false
library(tidyverse)



viome_file_path <- file.path(Sys.getenv("ONEDRIVE"),"General","Health","Microbiome","Viome","Viome Recommendations.xlsx")

viome_file_df <- readxl::read_excel(viome_file_path, na = "NA") %>% select(1:5)  # these happen to be Viome columns

recommendation_types <- factor(c("Avoid","Minimize","Enjoy","Superfood"))
levels(viome_file_df$`Oct-20`)<- recommendation_types
levels(viome_file_df$`Oct-22`)<- recommendation_types
levels(viome_file_df$`May-20`)<- recommendation_types
viome_file_df %>% head()
```

## Foods with the same recommendation as the last test

Remove non-Viome columns and any rows where results haven't changed for the last three tests.

```{r}
viome_file_df %>% count()
viome_file_df %>%  filter(`Oct-22`==`Oct-20`) %>% select(1:3)
```

## Foods whose recommendation has changed since the last test

```{r}

viome_file_df %>%  filter(`Oct-22`!=`Oct-20`) %>% select(1:3)

```

## Food recommendation counts per test

```{r}

x <- rbind(viome_file_df %>% count(`Oct-22`)  %>% t()  %>% as_tibble() %>% slice(2),
      viome_file_df %>% count(`Oct-20`) %>% (t) %>% as_tibble() %>% slice(2))
names(x) <- c(c("Avoid","Minimize","Enjoy","Superfood"),"NA")
x$date <- c("Oct-22","Oct-20")
x <- x %>% relocate(1:5,.after = last_col())
x %>% knitr::kable()
```
